%!TEX output_directory=dist
\documentclass[11pt, a4paper, sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}
% \setlength{\hintscolumnwidth}{4cm}
\usepackage{lmodern}
\usepackage{latexsym}
% \usepackage{amssymb} % for item symbols
% \usepackage[defaultfam,tabular,lining]{montserrat}
% \usepackage[T1]{fontenc}
\usepackage[scale=0.8, top=1.5cm, bottom=1.5cm]{geometry}

% \AtBeginDocument{\hypersetup{pdfborder = 0 0 1,linkcolor=blue}}
\renewcommand{\listitemsymbol}{$\, \bullet \,$ }
% \renewcommand{\rmdefault}{lmr}
% \renewcommand{\sfdefault}{lmss}
% \renewcommand{\ttdefault}{lmtt}
\renewcommand{\baselinestretch}{1} 
% \renewcommand*\oldstylenums[1]{{\fontfamily{Montserrat-TOsF}\selectfont #1}}

% blue color scheme colors
\definecolor{color0}{rgb}{0,0,0}% black
\definecolor{color1}{rgb}{0.22,0.45,0.70}% light blue
\definecolor{color2}{rgb}{0.45,0.45,0.45}% dark grey

% \titlespacing*{\section}
% {0pt}{5.5ex plus 1ex minus .2ex}{4.3ex plus .2ex}
\par%



\firstname{Dmitrii}
\familyname{Shikhaleev}
\address{Software Engineer}

\begin{document}
% TITLE
\textcolor{color1}{\textbf{\Huge Dmitrii Shikhaleev}} \par
\vspace{0.2cm}
\textcolor{color2}{\Large Software Engineer} \par
\vspace{0.2cm}

\textcolor{color2}{\small
    \href{tel:+905312587445}{+905312587445}
    % \hspace{0.2cm}
    $\bullet$
    % \hspace{0.2cm}
    \href{mailto://dmitrii.shikhaleev@gmail.com}{dmitrii.shikhaleev@gmail.com}
    % \hspace{0.2cm}
    $\bullet$
    % \hspace{0.2cm}
    Antalya, Turkey
}

\textcolor{color2}{\small
    \href{https://www.linkedin.com/in/dmitrii-shikhaleev}{linkedin.com/in/dmitrii-shikhaleev}
    $\bullet$
    \href{https://github.com/Padavan}{github.com/Padavan}
}

\vspace{0.4cm}

% PROFILE
\section{Profile}
Front-End Software Engineering professional with 5+ year of production experience. My main focus is on building products based on web technologies. I've been able to be flexible and deliver quickly. 


% SKILLS
\section{Skills}\addvspace{0.2cm}

\cvlistitem{Extensive experience and knowledge of the React ecosystem.}
\cvlistitem{Proficient working with JavaScript as well as TypeScript. Experience with Node.js and Electron.}
\cvlistitem{Worked with various State management systems for React - Redux, Mobx, Zustand, XState.}
\cvlistitem{Experience with GraphQL, REST.}
\cvlistitem{Experience with WebApi (Web Workers, Web Sockets, Chrome extension development).}
\cvlistitem{Solid understanding of CSS and CSS post/preprocessors.}
\cvlistitem{Experience with a variety of JS libraries (D3.js, moment.js, ag-grid, RxJS, lodash).}
\cvlistitem{Agile. Participation in Scrum activities, daily communication with the customer.}
\cvlistitem{Experience with Linux. Basic bash/python scripting and good understanding of UNIX tools.}
\cvlistitem{Know what CI/CD is. Builded Docker containers, worked with AWS services, kubernetes.}
\cvlistitem{Experienced in distributed development and remote collaboration.}
\cvlistitem{Languages. English - advanced, Russian - native}

% EXPERIENCE ----------------------------------------------------------------------------------------------------------
\section{Experience}

%% EPAM
\textbf{\Large EPAM Systems Inc.} \par\addvspace{0.1cm}
\cvitem{Software Engineer}{Jan 2019 --- Present}

\textit{EPAM Systems is a technology company that offers software engineering services for software development and digital platforms. I worked for a diverse range of clients in web development. Current and former clients include Adidas AG, Sygenta AG, Vizgen Inc, Mursion Inc.}
\vspace{0.2cm}

\cvlistitem{Have delivered multiple products to MVP/first customer stage.}
\cvlistitem{Participated in scrum activities: daily meetings with customers, sprint plannings, groomings, retrospectives, performed task breakdown, efforts estimation.}
\cvlistitem{Conducted demo sessions.}
\cvlistitem{Successfully maintained multiple long-term projects.}
\cvlistitem{Achieved self-sufficiency, so productivity wasn't decreased in absence of senior engineers.}
\cvlistitem{Deploying/Integrating cloud solutions.}
\cvlistitem{Implementing CI/CD pipeline.}
\cvlistitem{Implemented auth processes through SSO/cloud services.}
\cvlistitem{Implemented Microfrontend architecture based on Webpack Module Federation.}

\vspace{1em}
%% Chronist
\textbf{\Large Chronist LLC} \par\addvspace{0.1cm}
\cvitem{Software Engineer}{Jan 2017 --- Jan 2019}

\textit{Chronist is an educational online platform that offers interactive map and the possibility to travel in time on this map. Apart from that the system of layers allows users to create their own narratives based on the interconnections of certain events and environments.}
\vspace{0.2cm}

\cvlistitem{Took part in design discussions/decision-making processes.}
\cvlistitem{Implementing mockups for frontend interface for MVP.}
\cvlistitem{Built the landing page for the project.}
\cvlistitem{Made calculations and implementation for several animation and maps interaction tasks.}

% EDUCATION ------------------------------------------------------------------------------------------------------------
\section{Education}
\textbf{\Large Peter the Great St.Petersburg Polytechnic University} \par\addvspace{0.1cm}
\cvitem{Bachelor}{2008 --- 2016}
Electronics and Nanoelectronics

\vspace{9em}


\end{document}
