%!TEX output_directory=dist
\documentclass[11pt, a4paper, sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}
\usepackage{lmodern}
\usepackage{latexsym}
\usepackage[scale=0.8, top=1.5cm, bottom=1.5cm, left=1.5cm, right=1.5cm]{geometry}

% blue color scheme colors
\definecolor{color0}{rgb}{0,0,0}% black
\definecolor{color1}{rgb}{0.22,0.45,0.70}% light blue
\definecolor{color2}{rgb}{0.45,0.45,0.45}% dark grey

\name{Dmitrii}{Shikhaleev}
\title{Software Engineer} 
\address{Turkiye, Antalya}
\social[linkedin]{dmitrii.shikhaleev} 
\social[github]{Padavan}
\phone[mobile]{+7~(960)~240~8223}
\email{dmitrii.shikhaleev@gmail.com}

\begin{document}

\recipient{Company Recruitment team}{Company, Inc.\\123 somestreet\\some city}
\date{July 09, 2023}
\opening{Dear Hiring Team,}
\closing{Sincerely,}
\makelettertitle

I would like to submit my resume for your consideration regarding the position of
Innovation Product Associate/Engineer im Center of Expertise (ID: 171260).

I attained a bachelor’s degree in nanoelectronics at St. Petersburg Polytechnic University.
While doing so I’ve got interested in IT and new technologies which allowed me to attain
a strong foundation of technical skills including knowledge of operation systems and
programming languages such as C, Python, R and JavaScript. In my recent position I work
in a small team where I am responsible for development and optimization of web
application.

In my current position I constantly encounter complex problems, which I solve using
experience I collected working in different areas. I like to take on challenging tasks and I
perform well under pressure. I am used to work on projects that are outside my current
zone of expertise so I often have to acquire the knowledge needed in short time.
As an employee of a small company I would like to further challenge myself and work on
big-scaled projects in accordingly sized teams. {COMPANYNAME} as a worldwide leader in
business-oriented applications is such a company and I would gladly join and contribute
to its success.

Thank you for your time and consideration. I looking forward to speaking with you about
this opportunity.

\makeletterclosing

\end{document}
