\documentclass[11pt, a4paper]{article} 

\usepackage{lmodern}
\usepackage[sfdefault]{inter}
\usepackage{latexsym}
\usepackage{titlesec}
\usepackage{titling}
\usepackage{setspace}

% columns
\usepackage{blindtext}
\usepackage{multicol}

\usepackage[dvipsnames]{xcolor}

\definecolor{ColorBlack}{HTML}{000000}% black
\definecolor{ColorBlue}{HTML}{3873B3}% light blue
\definecolor{ColorGrey}{HTML}{333333}% darkdark grey
\definecolor{ColorLightGrey}{HTML}{DCDCDC}% darkdark grey
\definecolor{ColorGrey2}{HTML}{5A5A5A}


\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  linkcolor=ColorBlue,
  filecolor=magenta,      
  urlcolor=ColorBlack,
  pdftitle={Dmitrii Shikhaleev - CV},
  pdfpagemode=FullScreen,
}
\usepackage[margin=1cm]{geometry}
% \usepackage[defaultfam,light,tabular,lining]{montserrat} %% Option 'defaultfam'
\usepackage[skip=0pt plus1pt, indent=0pt]{parskip}

\makeatletter
\def\bfseries@sf{m}
\makeatother

\renewcommand*\oldstylenums[1]{{\fontfamily{Montserrat-TOsF}\selectfont #1}}

\title{CV}
\author{Dmitrii Shikhaleev}

% \setlength{\parindent}{0cm}

\titleformat{\section}
{\Large\bfseries\color{ColorBlack}}
{}
{0em}
{}[{\color{ColorLightGrey}\titlerule[2pt]}]

\newcommand{\cvdate}[1]{
  {\small\narrower\normalfont\color{ColorGrey2}{#1}}
}
\newcommand{\cvposition}[1]{\normalsize\textbf{#1}}
\newcommand{\cvcompany}[1]{\Large\textbf{#1}}
\newcommand{\cvproject}[1]{
  \begingroup
  \fontseries{sb}\color{ColorGrey2}\small{#1}
  \endgroup
}

\newcommand{\cventry}[3]{
  % \vspace{1em}
  \cvcompany{#1} \hfill \break
  \cvposition{#2} \hfill \cvdate{#3}\break 
  % \vspace{3pt}\hfill\break
  \vspace{-1em}
}

\renewcommand{\maketitle}{
  \noindent

  \begin{minipage}[t]{0.5\textwidth}
  \vspace{-\baselineskip} % Required for vertically aligning minipages
      {\Large\color{ColorGrey}\textbf{\theauthor}} \hfill\break
      Software Engineer \hfill\break
  \end{minipage}
  \hfill%
  \begin{minipage}[t]{0.5\textwidth}
  \begin{flushright}
  \vspace{-\baselineskip} % Required for vertically aligning minipages
    \href{mailto:dmitrii.shikhaleev@gmail.com}{dmitrii.shikhaleev@gmail.com} \\
    \href{tel:+905312587445}{+90~(531)~258~74~45} \\
    \href{http://t.me/padavanchik}{t.me/padavanchik} \\ 
    \href{https://www.linkedin.com/in/dmitrii-shikhaleev/}{linkedin.com/in/dmitrii-shikhaleev} \\
  \end{flushright}
  \end{minipage}

  \vspace{0.8em}
}

\newcommand{\cvlistitem}[1]{
  \begin{minipage}[t]{\textwidth}
  \strut\hspace{0.5em}\textcolor{ColorBlue}{\large\rmfamily\textbullet}\hspace{0.5em}#1
  \vspace{2pt}
  \end{minipage}
}

\pagenumbering{gobble}

\begin{document}
\maketitle
\setstretch{1.1}

Front-End Software Engineering professional with 5+ year of production experience. My main focus is on building products based on web technologies. I've been able to be flexible and deliver quickly. 

% SKILLS ------------------------------
\section{Skills / Technologies}

\cvlistitem{React, JavaScript/TypeScript, Node.JS, Electron, GraphQL, REST, WebSockets, AWS/GCP cloud infrastructure}%
\cvlistitem{Git, Docker, Nginx, Linux, Python Bash, Various CI/CD}%
\cvlistitem{Languages: English (Advanced), Russian (Native), German (Basic)}%

% EXPERIENCE --------------------------------
\section{Professional Experience}

%% EPAM
\cventry
{EPAM Systems Inc.}
{Software Engineer}
{Jan 2019 -- Present}

EPAM Systems is a technology company providing software engineering services for software development and digital platforms. I have worked for a wide range of clients (pharmaceutical, biotech, retail, edtech) in different positions (developer/key developer) and products in web development.
\break

\cvlistitem{Led a team of three developers, driving code reviews, and architectural decisions}
\cvlistitem{Improved system performance by introducing parallelism.}
\cvlistitem{Enhanced internal API, test coverage, and code reliability}
\cvlistitem{Integrated web application with cloud: AWS Cognito and AWS AppSync.}
\cvlistitem{Responsible for implementing socket connection, inter-process communication between electron app, local machine service and remote machine service.}
\cvlistitem{Facilitated the introduction of finite state machine state management to the project.}
\cvlistitem{Helped with communication between science team, web team and infrastructure team.}

%% Chronist
\cventry
{Chronist LLC.}
{Software Engineer}
{Jan, 2017 -- Jan, 2019}

Chronist is an online educational platform that offers an interactive map and the possibility to travel through time on this map.

\cvlistitem{Participation in design discussions/decision making processes.}
\cvlistitem{Implemented mock-ups for front-end interface for MVP.}
\cvlistitem{Created the landing page for the project.}
\cvlistitem{Calculated and implemented various animations and map interaction tasks.}

% EDUCATION
\section{Education}

\cventry{Peter the Great St.Petersburg Polytechnic University}{Bachelor}{Sep, 2008 -- Jun, 2016}
\cvlistitem{Electronics and Nanoelectronics}


\end{document}