%!TEX output_directory=dist
\documentclass[12pt, a4paper, sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}
\usepackage{lmodern}
\usepackage{latexsym}
% \usepackage{titling}
\usepackage[scale=0.8, top=1.5cm, bottom=1.5cm, left=1.5cm, right=1.5cm]{geometry}
\usepackage{etoolbox}

\definecolor{color0}{rgb}{0,0,0}% black
\definecolor{color1}{rgb}{0.22,0.45,0.70}% light blue
\definecolor{color2}{rgb}{0.45,0.45,0.45}% dark grey

\name{Dmitrii}{Shikhaleev}
\title{Software Engineer} 
\address{Turkiye, Antalya}
\social[linkedin]{dmitrii.shikhaleev} 
\social[github]{Padavan}
\phone[mobile]{+90~(531)~258~7445}
\email{dmitrii.shikhaleev@gmail.com}

\begin{document}
\maketitle

% PROFILE
\section{Profile}
Front-End Software Engineering professional with 5+ year of production experience. My main focus is on building products based on web technologies. I've been able to be flexible and deliver quickly. 

% SKILLS
\section{Skills}

\cvlistitem{Extensive experience and knowledge of the React ecosystem.}
\cvlistitem{Proficient working with JavaScript as well as TypeScript. Experience with Node.js and Electron.}
\cvlistitem{Worked with various State management systems for React - Redux, Mobx, Zustand, XState.}
\cvlistitem{Experience with GraphQL, REST.}
\cvlistitem{Experience with WebApi (Web Workers, Web Sockets, Chrome extension development).}
\cvlistitem{Solid understanding of CSS and CSS post/preprocessors.}
\cvlistitem{Experience with a variety of JS libraries (D3.js, moment.js, ag-grid, RxJS, lodash).}
\cvlistitem{Agile. Participation in Scrum activities, daily communication with the customer.}
\cvlistitem{Experience with Linux. Basic bash/python scripting and good understanding of UNIX tools.}
\cvlistitem{Know what CI/CD is. Builded Docker containers, worked with AWS services, kubernetes.}
\cvlistitem{Experienced in distributed development and remote collaboration.}
\cvlistitem{Languages. English - advanced, Russian - native}

% EXPERIENCE 
\section{Experience}

%% EPAM
\subsection{EPAM Systems Inc.}
\cvitem{Software Engineer}{Jan 2019 -- Present}

\textit{EPAM Systems is a technology company that offers software engineering services for software development and digital platforms. I worked for a diverse range of clients in web development. Current and former clients include Adidas AG, Sygenta AG, Vizgen Inc, Mursion Inc.}
\vspace{0.2cm}

\textit{Client: One of the biggest pharmaceutical company}
Sep, 2023 - Present

Key developer responsible to developing web application within bigdata development service.

\cvlistitem{Increased velocity in delivering new features}
\cvlistitem{Built up more efficient cooperation with backend teams}

\textit{Client: Pharmatech company}
Apr, 2023 – July, 2023

Key developer responsible for developing electron application with cloud SDK in short time with small team of 3 people.

\cvlistitem{Bootstrapped project, outlined software architecture, simplified credential management effort for client.}
\cvlistitem{Implemented clean communication process between different parts of the system.}
\cvlistitem{Improved system performance by introducing parallelism.}
\cvlistitem{Participated in development activities, code reviews, solution design, task breakdow, maintained documentation.}

\textit{Client: One of the biggest retail company}
Oct, 2021 – Dec, 2022

Frontend Developer on project to build marketing application \"Plan, Design and Manage Product domain.

\cvlistitem{Built and polished microfrontend web application with technogies such as React, mobx, ag-grid, webpack module federation}
\cvlistitem{Participated in scrum activities: daily meetings with the customer, sprint plannings, groomings, retrospectives, performed task breakdown, efforts estimation, conducted demo sessions}

\textit{Client: Biotechnology company}
Mar, 2021 - Sep, 2021

Developed two products: supporting web portal with gene data and Electron app to control science equipment.

\cvlistitem{Integrated web application with cloud: AWS Cognito and AWS AppSync.}
\cvlistitem{Responsible for implementing socket connection, inter process communication} between electron app, local machine service and remote machine service.
\cvlistitem{Facilitated Finite-State Machine state management introduction to the project.}
\cvlistitem{Helped with communication between science team, web team and infrastructure team}

\textit{Client: EdTech company.}
Jan, 2019 – Jul, 2020

Developing web application to schedule virtual training session, manage sessions, permissions and virtual assets.

\cvlistitem{Built and polished a dozen of customizable component and several key pages.}
\cvlistitem{Ensured that frontend part of the project is in aligned with permission restrictions and had good timezone support.}

%% Chronist
\subsection{Chronist LLC}
\cvitem{Software Engineer}{Jan 2017 -- Jan 2019}

\textit{Chronist is an educational online platform that offers interactive map and the possibility to travel in time on this map. Apart from that the system of layers allows users to create their own narratives based on the interconnections of certain events and environments.}
\vspace{0.2cm}

\cvlistitem{Took part in design discussions/decision-making processes.}
\cvlistitem{Implementing mockups for frontend interface for MVP.}
\cvlistitem{Built the landing page for the project.}
\cvlistitem{Made calculations and implementation for several animation and maps interaction tasks.}

% EDUCATION
\section{Education}
\subsection{Peter the Great St.Petersburg Polytechnic University}
\cvitem{Bachelor}{2008 -- 2016}
Electronics and Nanoelectronics

\end{document}
