\documentclass[11pt, a4paper, sans]{article} 

\usepackage{lmodern}
\usepackage{latexsym}
\usepackage{titlesec}
\usepackage{titling}
\usepackage{setspace}
\usepackage[dvipsnames]{xcolor}
\definecolor{ColorBlack}{rgb}{0,0,0}% black
\definecolor{ColorBlue}{rgb}{0.22,0.45,0.70}% light blue
\definecolor{ColorGrey}{RGB}{51,51,51}% darkdark grey
\definecolor{ColorLightGrey}{RGB}{220,220,220}% darkdark grey
\definecolor{ColorGrey2}{RGB}{90,90,90}

\usepackage[margin=1cm]{geometry}
% \usepackage[sfdefault]{inter} %% Option 'sfdefault' only if 'inter' is to be
% \usepackage[defaultfam,light,tabular,lining]{montserrat} %% Option 'defaultfam'
\usepackage[skip=10pt plus1pt, indent=0pt]{parskip}

\begin{document}

My name is Dmitrii. I have been a software engineer at EPAM for the past 5 years. I focus on building and delivering products based on web technologies. I'm quite flexible and collected a lot of experience working in different areas. 

My main strength lies is in the frontend stack with React and TypeScript. I devivered electron application and web application as well. using RESTful api and graphql api. I have production experience using it with various styling approaches, different state managment libraries, Different building system.

I have production experience with frontend and backend codebase. I've got cloud experience with Amazon and Google cloud infrastructure. I even got some devops experience working with managed k8s platform. So I know what CI/CD is, modern development methodologies (AGILE, SCRUM, KANBAN) and have a pretty good understanding of why testing is important. 

Education: As I lack formal computer science education I am trying to expand my horizons by trying new languages by solving problems on events like Advent of Code. I finish several courses on EPAM  like CloudX: Practiotioner for JS and Anglular Foundation. And I recently finished Algorithms courses on Coursera Platfrom.

Timeline Slide:
At this point I worked on 9 projects. At the slide you can see the most major ones. Most of them were green field projects. Five of them were delivered to MVP stage or version 1 or saw first users.
(MVP or version 1.0: merck, exscientia, adidas, vizgen, mursion)

Mursion: That is my first at EPAM and longest project so far. The project was about Web application to schedule virtual training sessions, manage sessions, permissions(ACL) and virtual assets for the EdTech company. I was responsible for building components with given design language and implementing some core features, code reviews. I witnessed heer migration from react class components to hooks. We were able to deliver MVP in time and next major version.

Epam. The next project was inner epam project. It was really understuffed so my role was extended a little. Frontend part was a simple page but with SSO integration. I was also trying to deliver our application to EPAM provided redhad openshift platform (managed k9s), setup ci/cd, automatic tests running. 

Vizgen: In the next project we were building Electron application to control scientific instruments and accompanying web application for biotech company. I was mostly responsible for development of electron application. I also wrote some python and bash scripts to glue electron app with remote linux box. and perfomed a role of bridge between science-team and electron team. We have been able to deliver MVP (what was platform protype). Photos of our platform with UI were in science magazines. That was cool. 
https://vizgen.com/products/

Adidas: 1 year and 2 month. Web application for the “Plan, Design, Manage Product“ domain large retail company. React, mobx, account in-house ui library, ag-grid library for tables, rxjs. Pretty standard. Build application, a lot of tables. There was like 10 frontend engineers. MVP was done, there were real users on some apps.

BCDT-PAYD: 2m month. I was here mainly to reduce technical debt on non-billable position. But it was really educational. Project was in such shape so you can't trust type system, typechecking wasn't strict. Can't trust openapi schema, it was written as afterthought for backend side. Can't trust ui-kit, it was still in development.
My task was to remove/replace legacy-components, implement strict typechecks. React/Typescript/OpenAPI. But due circumstances later I was reassigned to do business-related task without any onboarding and I was able to deliver.

Exscientia: Short Fixed-price contract type. Small team. This was tough project. We needed to build Electron application to manage experementation data on cloud infrastructure for pharmatech company.
I was only one engineer with cloud experience and electron application experience, so I participated everywhere. I Led a team of three developers, driving code reviews, architectural decisions, bootstraping electron aplpication and cloud infra and took part in development of majority of subsystems

Merck. And last project is My current project. We are building web application to manage ETL (Extract, transform, and load) jobs for large pharmaceutical companie. Pretty boring and standard on frontend side. I am trying to keep eye on backend part, openapi schema. Most of the big features development on me. Review process. I am facilitating simplification and test writing on my team.

\end{document}